DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
Wording abstract

\begin{abstract}
%
We present an automated MATLAB Toolbox, named as DSSynth (Digital-System
Synthesizer), to synthesize sound digital controllers for physical plants
that are represented as linear time-invariant systems with single input and
output.  In particular, DSSynth synthesizes digital controllers that are
sound w.r.t.  the stability and safety specifications by taking into account
finite word-length effects in their representation.  DSSynth considers the
complete range of approximations, including time discretization,
quantization effects, and finite-precision arithmetic (and its rounding
errors).  Currently, there are two DSSynth versions for synthesizing digital
controllers for physical plants represented by transfer function or
state-space equations: a command-line and a MATLAB application.  The
resulting toolbox enables application of program synthesis to real-world
control engineering systems.
%
\end{abstract}

>>>>

\begin{abstract}
%
We present an automated MATLAB Toolbox, named \emph{DSSynth} (Digital-System
Synthesizer), to synthesize sound digital controllers for physical plants
that are represented as linear time-invariant systems with single input and
output.  In~particular, DSSynth synthesizes digital controllers that are
sound w.r.t.~stability and safety specifications.  DSSynth considers the
complete range of approximations, including time discretization,
quantization effects and finite-precision arithmetic (and its rounding
errors).  The resulting toolbox enables the application of program synthesis
to real-world control engineering problems.
%
\end{abstract}
